The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-09-18 paper.tex
Fixed analysis of idiolect b and added diagram
Added all remaining diagrams

%\vspace{-3em}
%\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityanglehierarchydividingline1.9}}

\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.5 & {\sc *ComplexCoda} \\[0.5ex]
\hline \hline a. &   & \textipa{k1rm} & & $\ast$! \\
\hline b. & \ding{43} & \textipa{k1r1m} & 1.89 & \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
\end{tikzpicture}
}

@@

% TODO: diagram

@@

% TODO: scale

@@

% TODO: SonAngle diagram showing the various cut-off points.

The {\sc Sonority Rise} metric can achieve the same linear separation for idiolects 1, 3 and 4, but notice that this is not possible for idiolect \ref{CRNidiolect}, because {\sc Sonority Rise} cannot achieve a linear separation of the sonority rises, plateaus and RN from the remainder of the falling sonority clusters.

% TODO: SonRise diagram

@@

\begin{center}
\begin{tabular}{|l|ccc|c|cccc|} \hline
         & \multicolumn{3}{c|}{{\sc SonAngles}} &  & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
 Cluster & C1,C2 & C2,C3 & C3,C4 & Observed outcomes & 1 & 2 & 3 & 4 \\ \hline % TODO: name idiolects
 a. \textipa{sdBn} & 2.11 & 0.18 & 1.66 & \textipa{sd1Bn} & \multicolumn{4}{c|}{\textipa{sd1Bn}} \\ 
 b. \textipa{wzfn} & 2.03 & 1.33 & 0.54 & \textipa{wz1fn}, \textipa{w1zf1n} & \multicolumn{3}{c}{\textipa{wz1fn}} & \cellcolor{lightgray}  \textipa{w1zf1n} \\
 c. \textipa{gdfn} & 1.37 & 0.59 & 0.54 & \textipa{gd1fn}, \textipa{g1df1n} & \multicolumn{2}{c}{\textipa{gd1fn}} & \cellcolor{lightgray}  \textipa{g1df1n} &  \textipa{gd1fn} \\
 d. \textipa{mstn} & 2.03 & 2.11 & 0.27 & \textipa{m1st1n} & \multicolumn{2}{c}{*\textipa{ms1tn}} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{m1st1n}} \\
 e. \textipa{dmdn} & 0.27 & 2.36 & 0.27 & \textipa{d1md1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{d1md1n}} \\
 f. \textipa{drsn} & 0.12 & 2.21 & 0.54 & \textipa{d1rs1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{d1rs1n}} \\
 g. \textipa{sBxn} & 0.34 & 2.17 & 0.54 & \textipa{s1Bx1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{s1Bx1n}} \\
 h. \textipa{kftn} & 0.59 & 2.11 & 0.27 & \textipa{k1ft1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{k1ft1n}} \\
 i. \textipa{ktfn} & 1.37 & 0.59 & 0.54 & \textipa{kt1fn}, \textipa{k1tf1n} & \multicolumn{2}{c}{\textipa{kt1fn}} & \cellcolor{lightgray}  \textipa{k1tf1n} &  \textipa{kt1fn} \\
 j. \textipa{sgdn} & 2.11 & 1.37 & 0.27 & \textipa{sg1dn}, \textipa{s1gd1n} & \multicolumn{3}{c}{\textipa{sg1dn}} & \cellcolor{lightgray}  \textipa{s1gd1n} \\
 k. \textipa{srBn} & 0.22 & 1.57 & 1.65 & \textipa{sr1Bn}, \textipa{s1rB1n} & \multicolumn{2}{c}{\textipa{sr1Bn}} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{s1rB1n}} \\
 l. \textipa{krmn} & 0.12 & 1.89 & 1.25 & \textipa{kr1mn}, \textipa{k1rm1n} & \cellcolor{lightgray}  \textipa{k1rm1n} & \textipa{kr1mn} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{k1rm1n}} \\ \hline
 \end{tabular}
\end{center}

@@

\section{Disregarding V-C2}

>>>>

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
  \tikzstyle{line} = [draw, -latex']

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {bF};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
\end{tikzpicture}
}

\ex. {\sc Ident(SonAngle)}$<$1.9 $\gg$ {\sc *ComplexCoda}

\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/\textipa{k1rm}/} & {\sc Ident(SonAngle)}$<$1.9 & {\sc *ComplexCoda} \\[0.5ex]
\hline \hline a. &   & \textipa{k1rm} & & $\ast$! \\
\hline b. & \ding{43} & \textipa{k1r1m} & 1.89 & \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
\end{tikzpicture}
}

@@

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{vertex}=[circle]
  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (3*3,2.0)   {RT};
  \node (NT) at (2*3,1.5)  {NT};
  \node (FT) at (1*3,1.0)  {FT};
  \node (TT) at (0*3,0.5)     {TT};
  \node (RF) at (2*3,2.0)     {RF};
  \node (NF) at (1*3,1.5)  {NF};
  \node (FF) at (0*3,1.0)   {FF};
  \node (TF) at (-1*3,0.5)   {TF};
  \node (RN) at (1*3,2.0)   {RN};
  \node (NN) at (0*3,1.5)   {NN};
  \node (FN) at (-1*3,1)  {FN};
  \node (TN) at (-2*3,0.5)   {TN};
  \node (RR) at (0*3,2.0)  {RR};
  \node (NR) at (-1*3,1.5)  {NR};
  \node (FR) at (-2*3,1.0)   {FR};
  \node (TR) at (-3*3,0.5)   {TR};
  % headers
  \node (rising) at (2*3,2.6) {\underline{Falling sonority}};
  \node (level) at (0*3,2.6) {\underline{Level sonority}};
  \node (falling) at (-2*3,2.6) {\underline{Rising sonority}};
  % axis
  \node (axisstart) at (-3.5*3,-0) {};
  \node (axisend)   at (3.5*3,-0) {};
  \draw (axisstart) -- (axisend);
  \draw (0, 0.2) -- (0, -0.2) -- cycle;
  \draw (1*3, 0.2) -- (1*3, -0.2) -- cycle;
  \draw (2*3, 0.2) -- (2*3, -0.2) -- cycle;
  \draw (3*3, 0.2) -- (3*3, -0.2) -- cycle;
  \draw (-1*3, 0.2) -- (-1*3, -0.2) -- cycle;
  \draw (-2*3, 0.2) -- (-2*3, -0.2) -- cycle;
  \draw (-3*3, 0.2) -- (-3*3, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*3,-0.5) {1};
  \node (2pointlabel) at (2.0*3,-0.5) {2};
  \node (3pointlabel) at (3.0*3,-0.5) {3};
  \node (-1pointlabel) at (-1.0*3,-0.5) {-1};
  \node (-2pointlabel) at (-2.0*3,-0.5) {-2};
  \node (-3pointlabel) at (-3.0*3,-0.5) {-3};
  \node (xaxislabel) at (3.5*3,-0.5) {\textsc{Dis}};
\end{tikzpicture}
}

@@

@@

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{point}=[circle,fill=black!25,minimum size=12pt,inner sep=2pt]
  \tikzstyle{line} = [draw, -latex']

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {bF};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
  \node (dividingpointlabel2) at (1.9*8, -1.0) {\ref{CRNidiolect}};
  % another dividing line
  \node (dividingline2start) at (1.5 * 8,2) {};
  \node (dividingline2end)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividingline2start) -- (dividingline2end) -- cycle;
  \node (dividingpoint2label) at (1.5*8, -0.5) {1.5};
  \node (dividingpoint2label2) at (1.5*8, -1.0) {\ref{defaultCCCidiolect} \& \ref{C1CCidiolect}};
  % third dividing line
  \node (dividingline3start) at (1.0 * 8,2) {};
  \node (dividingline3end)   at (1.0 * 8,-0.3) {};
  \path [line,dashed] (dividingline3start) -- (dividingline3end) -- cycle;
  \node (dividingpoint3label2) at (1.0*8, -1.0) {\ref{wizfidiolect}};
\end{tikzpicture}
}

\bigskip
The {\sc Sonority Rise} metric can achieve the same linear separation for idiolects \ref{defaultCCCidiolect}, \ref{C1CCidiolect} and \ref{wizfidiolect}, but notice that this is not possible for idiolect \ref{CRNidiolect}, because {\sc Sonority Rise} cannot achieve a linear separation of the sonority rises, plateaus and RN from the remainder of the falling sonority clusters.

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
\end{tikzpicture}
}
\bigskip

@@

\begin{center}
\begin{tabular}{|l|ccc|c|cccc|} \hline
         & \multicolumn{3}{c|}{{\sc SonAngles}} & Observed & \multicolumn{4}{c|}{{\sc Predictions of idiolect}} \\
 Cluster & C1,C2 & C2,C3 & C3,C4 &  outcomes & \ref{defaultCCCidiolect} & \ref{CRNidiolect} & \ref{C1CCidiolect} & \ref{wizfidiolect} \\ \hline 
 a. \textipa{sdBn} & 2.11 & 0.18 & 1.66 & \textipa{sd1Bn} & \multicolumn{4}{c|}{\textipa{sd1Bn}} \\ 
 b. \textipa{wzfn} & 2.03 & 1.33 & 0.54 & \textipa{wz1fn}, \textipa{w1zf1n} & \multicolumn{3}{c}{\textipa{wz1fn}} & \cellcolor{lightgray}  \textipa{w1zf1n} \\
 c. \textipa{gdfn} & 1.37 & 0.59 & 0.54 & \textipa{gd1fn}, \textipa{g1df1n} & \multicolumn{2}{c}{\textipa{gd1fn}} & \cellcolor{lightgray}  \textipa{g1df1n} &  \textipa{gd1fn} \\
 d. \textipa{mstn} & 2.03 & 2.11 & 0.27 & \textipa{m1st1n} & \multicolumn{2}{c}{*\textipa{ms1tn}} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{m1st1n}} \\
 e. \textipa{dmdn} & 0.27 & 2.36 & 0.27 & \textipa{d1md1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{d1md1n}} \\
 f. \textipa{drsn} & 0.12 & 2.21 & 0.54 & \textipa{d1rs1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{d1rs1n}} \\
 g. \textipa{sBxn} & 0.34 & 2.17 & 0.54 & \textipa{s1Bx1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{s1Bx1n}} \\
 h. \textipa{kftn} & 0.59 & 2.11 & 0.27 & \textipa{k1ft1n} & \multicolumn{4}{c|}{\cellcolor{lightgray} \textipa{k1ft1n}} \\
 i. \textipa{ktfn} & 1.37 & 0.59 & 0.54 & \textipa{kt1fn}, \textipa{k1tf1n} & \multicolumn{2}{c}{\textipa{kt1fn}} & \cellcolor{lightgray}  \textipa{k1tf1n} &  \textipa{kt1fn} \\
 j. \textipa{sgdn} & 2.11 & 1.37 & 0.27 & \textipa{sg1dn}, \textipa{s1gd1n} & \multicolumn{3}{c}{\textipa{sg1dn}} & \cellcolor{lightgray}  \textipa{s1gd1n} \\
 k. \textipa{srBn} & 0.22 & 1.57 & 1.65 & \textipa{sr1Bn}, \textipa{s1rB1n} & \multicolumn{2}{c}{\textipa{sr1Bn}} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{s1rB1n}} \\
 l. \textipa{krmn} & 0.12 & 1.89 & 1.25 & \textipa{kr1mn}, \textipa{k1rm1n} & \cellcolor{lightgray}  \textipa{k1rm1n} & \textipa{kr1mn} & \multicolumn{2}{c|}{\cellcolor{lightgray}  \textipa{k1rm1n}} \\ \hline
 \end{tabular}
\end{center}

@@

\subsection{Disregarding V-C2}
